Global optimization method with dual Lipschitz constant estimates for problems with non-convex constraints

### 2020-01-09 2019/NUMTA_Barkalov/Special Issure/article.tex
Some minor changes to compile LaTeX

$$\[
	\psi(x)=\frac{g_{\nu}(y(x))}{K_{\nu}} - 
	\left\{
   \begin{array}{lr}
     0, & \nu \leq m,\\
     \frac{\varphi^*}{K_{m+1}}, & \nu = m + 1.
   \end{array}
	\right
\]$$

@@

\cite{Evtushenko, Piyavskii1972, Strongin1970, Shubert1972, Evtushenko2009, Evtushenko2013, Strongin2000, Sergeyev2013, Pinter1996, Jones2009, Wood1991, Meewella1988, Mladineo1986, Vaz2009, Stripinis2019, Paulavicius2016, Pillo2012, Pillo2016, Barkalov2017_1, Barkalov2017_2, Sergeyev2006, Zilinskas2008, Sovrasov2019}.

>>>>

\begin{eqnarray}
	\psi(x)=\frac{g_{\nu}(y(x))}{K_{\nu}} - 
	\left\{
   \begin{array}{lr}
     0, & \nu \leq m,\\
     \frac{\varphi^*}{K_{m+1}}, & \nu = m + 1.
   \end{array}
	\right.
\end{eqnarray}

@@

\cite{Evtushenko, Piyavskii1972, Shubert1972, Evtushenko2009, Evtushenko2013, Strongin2000, Sergeyev2013, Pinter1996, Jones2009, Wood1991, Meewella1988, Mladineo1986, Vaz2009, Stripinis2019, Paulavicius2016, Pillo2012, Pillo2016, Barkalov2017_1, Barkalov2017_2, Sergeyev2006, Zilinskas2008, Sovrasov2019}.
